Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex
Cleaned up later part of the Communities section; the intent of those sections definitely met by the Kitware story and the cases presented in the cross-cutting section.
Fix typo.

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

\subsubsection{Admirable scientific software communities}
\begin{itemize}
\item example communities
\item their (quick) origin stories.
\end{itemize}

\subsubsection{Resources for learning about software communities}

>>>>

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

\subsubsection{Additional Resources for learning about software communities}
